---
title: "Is the effect of Level on Error Time Moderated by Fugl-Meyer Scores?"
output: html_notebook
---

### Import Libraries into session:

```{r}
library(readxl)
library(dplyr)
library(tidyverse)
library(lme4)
library(ggplot2)
library(viridis)
library(tinythemes)
library(flexplot)
```

### Load Outcome Data:

```{r}
data <- read_excel("~/Jazz Pharma Prep/test datasets/Plos One Devin Austin Dataset.xlsx",
                            sheet = "Data-Individuals_with_stroke", 
                            skip = 1)
head(data)
```

### Load Clincial Data:

```{r}
clinical_data <- read_excel("~/Jazz Pharma Prep/test datasets/Plos One Devin Austin Dataset.xlsx",
                            sheet = "Clinical_Information")
head(clinical_data)
```

### Compile Clinical + Outcome Data into Long Format:

```{r}
n_levels <- 8
n_subjects <- 20
subject_labels <- rep(pull(data, Participant), times = n_levels)
level_1_error_time <- select(data, contains("ET_L1")) %>%  apply(1,mean, na.rm = TRUE)
level_2_error_time <- select(data, contains("ET_L2")) %>%  apply(1,mean, na.rm = TRUE)
level_3_error_time <- select(data, contains("ET_L3")) %>%  apply(1,mean, na.rm = TRUE)
level_4_error_time <- select(data, contains("ET_L4")) %>%  apply(1,mean, na.rm = TRUE)
level_5_error_time <- select(data, contains("ET_L5")) %>%  apply(1,mean, na.rm = TRUE)
level_6_error_time <- select(data, contains("ET_L6")) %>%  apply(1,mean, na.rm = TRUE)
level_7_error_time <-  select(data, contains("ET_L7")) %>%  apply(1,mean, na.rm = TRUE)
level_8_error_time <-  select(data, contains("ET_L8")) %>%  apply(1,mean, na.rm = TRUE)
error_time <- c(level_1_error_time,
  level_2_error_time, 
  level_3_error_time,
  level_4_error_time,
  level_5_error_time,
  level_6_error_time,
  level_7_error_time,
  level_8_error_time
)
level_labels <-  rep(1:n_levels, each = n_subjects)
fma_values <- rep(pull(clinical_data, FMA), times = n_levels)
# fma_values_categorical <- ifelse(fma_values >= 53, "mild", "moderate_severe")

error_time_dataset <-  data.frame(Subject = subject_labels, Levels = level_labels, FMA = fma_values, Error_Time = error_time)
head(error_time_dataset)
```

### Visualize Data:

```{r fig.height=6, fig.width=10}
ggplot(data = error_time_dataset, aes(x = Subject, y = Levels, fill = Error_Time)) + 
  geom_tile(lineend = "round", linejoin = "bevel", color = "gray") +
  scale_y_continuous(name="Days", breaks = seq(1, 8, 1)) + 
  scale_x_continuous(name="Subject", breaks = seq(1, 20, 1)) + 
  coord_fixed() +
  theme(panel.grid.major = element_blank(),panel.grid.minor = element_blank(),
        panel.background = element_blank(), plot.title = element_text(size = 20), 
        text = element_text(size = 20),
        axis.text.x = element_text(angle = 45, vjust = 1.5, hjust = 1),
        legend.key.height = unit(1, "cm"))
```

#### Notes:

-   Subject 5 is missing data for level 2

-   Referencing subject notes tells us that Subject 5 was heavily fatigued and did not complete level 2

-   Since Subject 5, level 2 is not missing at random, we exclude the subject entirely

```{r}
error_time_dataset_no5 <- 
  error_time_dataset %>%
  filter(Subject != 5)

nrow(error_time_dataset)
nrow(error_time_dataset_no5)
```

### Create Baseline Model:

-   Model description:

    -   Error Time depends on level difficulty and upper limb impairment level, while assuming each subject reacts differently to harder mazes.

```{r}
model_baseline <- lmer(Error_Time ~ Levels + FMA + (Levels|Subject),
                       data = error_time_dataset_no5)
summary(model_baseline)
```

```{r}
visualize(model_baseline, plot= "model", sample = 20)
```

### Create Full Model:

-   Model description:

    -   Error Time depends on maze difficulty x impairment interaction, with each subject having their own maze difficulty response.

        -   Maze difficulty x impairment interaction: changes in upper limb impairment level effect how difficult a level is

```{r}
model_full <- lmer(Error_Time ~ Levels*FMA + (Levels|Subject),
                   data = error_time_dataset_no5)

summary(model_full)
```

```{r}
visualize(model_full, plot= "model", sample = 20)
```

### Compare Models:

```{r}
moderation_test <- anova(model_baseline, model_full)
print(moderation_test)
```

```{r fig.height=6, fig.width=10}
predicted_baseline <- predict(model_baseline)
predicted_full <- predict(model_full)

df <- data.frame(Observed = error_time_dataset_no5$Error_Time,
                 Predicted_1 = predicted_baseline,
                 Predicted_2 = predicted_full)

ggplot(df, aes(x = Observed)) +
  geom_point(aes(y = Predicted_1, color = 'blue'), alpha = .5, size = 2) +
  geom_point(aes(y = Predicted_2, color = 'red'), alpha = .5, size = 2) +
  geom_abline(intercept = 0, slope = 1,
              linetype = "dashed") + 
  scale_color_manual(labels = c("Model 1", "Model 2"), values = c("blue", "red")) +
  theme(panel.grid.major = element_blank(),panel.grid.minor = element_blank(),
        panel.background = element_blank(), plot.title = element_text(size = 20), 
        text = element_text(size = 20),
        axis.title.x = element_text(size = 20),
        legend.title=element_blank()) + 
  xlab("Observed") + 
  ylab("Predicted") +
  ggtitle("Model Predictions") + 
  coord_fixed(ratio = 1)
```
